Policy optimization for dynamic spatiotemporal systems \hspace{1em} \insertframenumber

### 2014-09-15 pot/LaTeX/skewnormal.tex
more data analysis settings

\subsection{Model comparisons}
We fit the model using Gaussian and skew-$t$ marginal distributions, $K=1, 5, 10, 15$ partitions, with $Y(\bs)$ censored at $T = 0, 50, 75, 90$ ppb as described in Section \ref{s:data}.
We also include a max-stable analysis using the method by ????
All methods assume the mean function given in (\ref{eq:datamean}).
For each model, Brier scores and quantile scores were were averaged over all sites and days to obtain a single quantile score for each dataset.
At a particular threshold or quantile level, the model that fits the best is the one with the lowest score.
Looking at the heatplot in Figure \ref{fig:heatplot}, we can see that the methods using no thresholding tend to outperform those methods that do use thresholding.
\hl{Brian, I'm not sure that this is the best way to show this. Maybe a better heatplot would be quantile scores for $T=0$ for a few different quantiles. Then you can get a sense how the partitions impact the scores. The main problem is that $K=10, T=q(0.90)$ is much larger (5 - 7 times) than the rest of the quantile scores (across all values), so it really has an impact on the color scale}

>>>>

\subsection{Model comparisons}
We fit the model using Gaussian and skew-$t$ marginal distributions, $K=1, 5, 10, 15$ partitions, with $Y(\bs)$ censored at $T = 0, 50, 75, 90$ ppb as described in Section \ref{s:data}.
We also include a max-stable analysis using the method by ????
All methods assume the mean function given in (\ref{eq:datamean}).
For each model, Brier scores and quantile scores were were averaged over all sites and days to obtain a single quantile score for each dataset.
At a particular threshold or quantile level, the model that fits the best is the one with the lowest score.
Looking at the heatplot in Figure \ref{fig:heatplot}, we can see that the methods using no thresholding tend to outperform those methods that do use thresholding.
